Hydras \& Co.

### 2022-03-18 doc/part-hydras.tex
corrections chapter 6 (up to page 130)

@@

We may say that the interval $[6,700]$ is $\omega^2$-large, since it leads to $0$, but nothing assures us that the condition of minimality is satisfied.

@@

For instance, we prove that the interval $[6,510]$ is $\omega^2$-mlarge.

@@

Our exploration of the $L_\alpha$\,s  considers the usual cases of a proof by transfinite induction: zero, successors and limit ordinals. The lemmas we are going to proved will be applied in a big proof by induction in Sect~\vref{sect:L-correct-proof}.

@@

By iterating the functional \texttt{L\_succ}, we get a realization of
\texttt{(L\_spec (fin $i$))} for any natural number $i$.

@@

The following lemma expresses the length of the mlarge sequences associated with the finite multiples of $\omega$.

@@

\subsubsection{Going further}
Let us consider a last example, ``computing'' $L_{\omega^3}$.
Since the canonical sequence associated with this ordinal is composed of the
$\omega^2\times i\;(i\in\mathbb{N}_1)$, we have to study this sequence.

@@

\inputsnippets{Large_Sets/phi0Mult, Large_Sets/phi0MultOk,
Large_Sets/Phi0MultSLe}

>>>>

\input{movies/snippets/Large_Sets/mlargeDef}

@@

@@

@@

Our exploration of the $L_\alpha$\,s  considers the usual cases of a proof by transfinite induction: zero, successors and limit ordinals. The lemmas we are going to prove will be applied in a big proof by induction in Sect~\vref{sect:L-correct-proof}.

@@

By iterating the functional \texttt{L\_succ}, we get a realization of
\texttt{(L\_spec $i$)} for any natural number $i$.

@@

The following lemma expresses the length of the mlarge sequences associated with any finite multiple of $\omega$.

@@

\subsubsection{Going further}
Let us consider a last example, ``computing'' $L_{\omega^3}$.
Let us study the canonical sequence associated with $\omega^3$, the elements of which are 
$\omega^2\times i\;(i\in\mathbb{N}_1)$.

@@

\inputsnippets{Large_Sets/phi0Mult}

\inputsnippets{Large_Sets/phi0MultOk,
Large_Sets/Phi0MultSLe}
